---
title: "Lab5 HW Assignment C.Thomas"
author: "Charlene Thomas"
date: "October 14, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Assignment - Lab5

1. Modify your function from the Problem 2 (Lab5 Activity). The function should simulate N rounds of the game (instead of just one) and return the proportion of times you win the bet. Run the function with N = 1000 and 10000.

```{r}
game <- function(n) {
  wins = 0
  rounds <- replicate(n, {
  x <- sample(1:6, 6, replace = TRUE)
  }
  )
  for(i in 1:ncol(rounds)) {
   if (6 %in% rounds[,i]) {
    wins = wins + 1 
   }
  }
  return(wins/n)
}
game(1000)
game(10000)

```


2. Write a function that will find the smallest element of a given vector (built-in min() is not allowed). Your function should return the smallest element and index of the smallest element.
Ex. vector is (1, 4, 2, 0, 5), then the smallest element - 0 and index is 4.

```{r}

min.location <- function(x) {
  min.value <- x[1]
  for (i in seq_along(x[-1])+1)
    if (x[i] < min.value) {
      min.value <- x[i]
    }
  output1 <-list("Smallest Element" = min.value, "Index of Smallest Element" = i)
  return(output1)
}
love <- c(4,5,6,7,8,3)
min.location(love)
```

